DOpElib: Differential Equations\\ and Optimization Environment

### 2013-05-09 Examples/Documentation/introduction.tex
Updated docu to new wrapper files
Added and corrected Doxygen comments

\subsubsection{IPOPT}
If you would like to use the optimization routines offered by IPOPT
\url{https://projects.coin-or.org/Ipopt} you can  
install this yourself and add a symlink as described in \texttt{ThirdPartyLibs/README}.
Alternatively, you can use installation script
\texttt{ThirdPartyLibs/install-free-libs.sh}. Note that to use all 
available linear solvers you may have to obtain a corresponding license 
manually. This is true in particular for the HSL solvers MA27, $\ldots$.
For information on these see the information provided by the installation
script.

@@

\subsection{Reduced problems (Solve the PDE)}
At times it is nice to remove the PDE constraint in (OPT). 
This is handled by so called reduced 
problems (for algorithmic aspects we refer the reader to 
\cite{BeMeVe06}). 
This means that the reduced problem implicitly solves the PDE whenever required
and eliminates the variable $u$ from the problem.
\begin{itemize}
\item \texttt{reducedproblems/statpdeproblem.h} This is used to remove the variable $u$ in 
  a stationary PDE problem. This means that call the method \\
  \texttt{StatPDEProblem::ComputeReducedFunctionals} will evaluate the functionals 
  defined in the problem description, i.e., in \texttt{PDEProblemContainer}, in the 
  solution of the given PDE.
\item \texttt{reducedproblems/statreducedproblem.h} This eliminates $u$ from the OPT
  problem with a stationary PDE.
\item \texttt{reducedproblems/instatreducedproblem.h} The same as above but for a
  nonstationary PDE.
\item \texttt{reducedproblems/voidreducedproblem.h} A wrapper file that eliminates $u$ 
  if it is not present anyways. This is used so that we can use the same routines to 
  solve problems that have no PDE constraint.
\item \texttt{reducedproblems/ipopt\underline{ }problem.h} A wrapper file that is used by the 
  reduced\underline{ }ipopt\underline{ }algorithm when solving optimization problems. This file
  hides the interface to IPOPT.
\end{itemize}

@@

\subsubsection{Constraints and system matrix}
\begin{itemize}
\item \texttt{include/userdefineddofconstraints.h} This class sets the constraints on the DOFs of the state and/or control FE solution. DOpE itself builds the hanging-node-constraints, but the user can reimplement this class and thus include other constraints as well (for example periodic BC). Note, that the hanging-node-constraints come first (in case of conflicting constraints.)
\item \texttt{include/sparsitymaker.h} This class sets the sparsity pattern for the state FE solution. The standard implementation is just a wrapper for \texttt{dealii::DoFTools::} \texttt{make\_sparsity\_pattern}, but the user can reimplement this class to allow for more sophisticated sparsity patterns.
\item \texttt{include/pointconstraintsmaker.h} This class is derived from \texttt{include/userdefineddofconstraints.h}
  and allows to set homogeneous dirichlet values at given points/components.
\end{itemize}

@@

\subsubsection{Auto-generated Problem Descriptions}
\begin{itemize}
  \item \texttt{problemdata/stateproblem.h} This is the problem description for the (forward/primal) PDE constraint.
    {\bf Similar descriptors will be build for the other problems (adjoint, tangent, $\ldots$) when time allows.}
  \item \texttt{problemdata/initialproblem.h} This is the problem descriptor to compute the finite element representation
    of the initial values. This is generated by the different time-stepping schemes based upon the defined 
    representation by the pde, which is set to the component wise $L^2$ projection by default.
  \item \texttt{problemdata/primaldirichletdata.h} This class contains the Dirichlet data for the 
    forward/primal PDE.
  \item \texttt{problemdata/tangentdirichletdata.h} This class contains the Dirichlet data for the tangent PDE, i.e.,
    the first derivative of the Dirichlet data.
  \item \texttt{problemdata/transposedgradientdirichletdata.h} This contains the transposed Dirichlet data needed 
    to calculate the gradient of the reduced objective functional, 
    for detail see \texttt{interfaces/transposeddirichletdatainterface.h}.
  \item \texttt{problemdata/transposedhessiandirichletdata.h} This contains the transposed Dirichlet data needed 
    to calculate the hessian of the reduced objective functional, 
    for detail see \texttt{interfaces/transposeddirichletdatainterface.h}.
\end{itemize}
\subsubsection{Management of Time Dependent Problems}
\begin{itemize}
\item \texttt{include/timedofhandler.h} DoFHandler responsible for the management of the timedofs (this is a part of the \texttt{SpaceTimeDoFHandler}-classes). Basically a wrapper for a $1d$ \texttt{deal.II}-DoFHandler.
\item \texttt{include/timeiterator.h} This class works as an iterator on the \texttt{TimeDoFHandler}.                 
\end{itemize}
\subsection{Wrapper classes}
\begin{itemize}
  \item \texttt{wrapper/dofhandler\underline{ }wrapper.h} A wrapper class for the \texttt{deal.II} DoFHandlers. This 
    class is needed to provide support for the \texttt{dim $= 0$} case and to have a uniform interface to 
    DoFHandler and HPDoFHandler.
  \item \texttt{wrapper/fevalues\underline{ }wrapper.h} {\bf Will be removed soon!}
  \item \texttt{wrapper/function\underline{ }wrapper.h} An interface that allows to use functions that depend 
    not only on space but also on time.
  \item \texttt{wrapper/mapping\underline{ }wrapper.h} An interface that allows to use \texttt{deal.II}-mappings as well as  \texttt{deal.II}-mapping collections depending of the DoFHandler in use. To this end, the class has a template parameter \texttt{DOFHANDLER}.
  \item \texttt{wrapper/preconditioner\underline{ }wrapper.h} Contains wrappers for several of the preconditioners
    in \texttt{deal.II}. This is required since unfortunately the preconditioners in \texttt{deal.II} have different
    interfaces for their initialization.
  \item \texttt{wrapper/snopt\underline{ }wrapper.h} An interface to the SNOPT fortran library. This is an additional
    wrapper to the one provided by SNOPT to allow automatic construction of the functions required 
    by SNOPT using our library.
\end{itemize}

>>>>

\subsubsection{IPOPT}
If you would like to use the optimization routines offered by IPOPT
\url{https://projects.coin-or.org/Ipopt} you can  
install this yourself and add a symlink as described in \texttt{ThirdPartyLibs/README}.

Alternatively, you can use installation script
\texttt{ThirdPartyLibs/install-free-libs.sh}. Note that to use all 
available linear solvers you may have to obtain a corresponding license 
manually. This is true in particular for the HSL solvers MA27, $\ldots$.
For information on these see the information provided by the installation
script.

@@

\subsection{Reduced problems (Solve the PDE)}
At times it is nice to remove the PDE constraint in (OPT). 
This is handled by so called reduced 
problems (for algorithmic aspects we refer the reader to 
\cite{BeMeVe06}). 
This means that the reduced problem implicitly solves the PDE whenever required
and eliminates the variable $u$ from the problem.
\begin{itemize}
\item \texttt{reducedproblems/statpdeproblem.h} This is used to remove the variable $u$ in 
  a stationary PDE problem. This means that call the method \\
  \texttt{StatPDEProblem::ComputeReducedFunctionals} will evaluate the functionals 
  defined in the problem description, i.e., in \texttt{PDEProblemContainer}, in the 
  solution of the given PDE.
\item \texttt{reducedproblems/statreducedproblem.h} This eliminates $u$ from the OPT
  problem with a stationary PDE.
\item \texttt{reducedproblems/instatreducedproblem.h} The same as above but for a
  nonstationary PDE.
\item \texttt{reducedproblems/voidreducedproblem.h} A wrapper file that eliminates $u$ 
  if it is not present anyways. This is used so that we can use the same routines to 
  solve problems that have no PDE constraint.
\item \texttt{reducedproblems/ipopt\underline{ }problem.h} A wrapper file 
 required when solving optimization problems using the 
  reduced\underline{ }ipopt\underline{ }algorithm. This file
  hides the interface to IPOPT.
\end{itemize}

@@

\subsubsection{Constraints and system matrix}
\begin{itemize}
\item \texttt{include/userdefineddofconstraints.h} This class sets the constraints on the DOFs of the state and/or control FE solution. DOpE itself builds the hanging-node-constraints, but the user can reimplement this class and thus include other constraints as well (for example periodic BC). Note, that the hanging-node-constraints come first (in case of conflicting constraints.)
\item \texttt{include/sparsitymaker.h} This class sets the sparsity pattern for the state FE solution. The standard implementation is just a wrapper for \texttt{dealii::DoFTools::} \texttt{make\_sparsity\_pattern}, but the user can reimplement this class to allow for more sophisticated sparsity patterns.
\item \texttt{include/pointconstraintsmaker.h} This class allows to set 
  homogeneous dirichlet values at given points/components.
\end{itemize}

@@

\subsubsection{Auto-generated Problem Descriptions}
\begin{itemize}
  \item \texttt{problemdata/stateproblem.h} This is the problem description for the (forward/primal) PDE constraint.
    {\bf Similar descriptors will be build for the other problems (adjoint, tangent, $\ldots$) when time allows.}
  \item \texttt{problemdata/initialproblem.h} This is the problem descriptor to compute the finite element representation
    of the initial values. This is generated by the different time-stepping schemes based upon the defined 
    representation by the pde, which is set to the component wise $L^2$ projection by default.
  \item \texttt{problemdata/primaldirichletdata.h} This class contains the Dirichlet data for the 
    forward/primal PDE.
  \item \texttt{problemdata/tangentdirichletdata.h} This class contains the Dirichlet data for the tangent PDE, i.e.,
    the first derivative of the Dirichlet data.
  \item \texttt{problemdata/transposedgradientdirichletdata.h} This contains the transposed Dirichlet data needed 
    to calculate the gradient of the reduced objective functional, 
    for detail see \texttt{interfaces/transposeddirichletdatainterface.h}.
  \item \texttt{problemdata/transposedhessiandirichletdata.h} This contains the transposed Dirichlet data needed 
    to calculate the hessian of the reduced objective functional, 
    for detail see \texttt{interfaces/transposeddirichletdatainterface.h}.
\end{itemize}
\subsubsection{Management of Time Dependent Problems}
\begin{itemize}
\item \texttt{include/timedofhandler.h} DoFHandler responsible for the management of the timedofs (this is a part of the \texttt{SpaceTimeDoFHandler}-classes). Basically a wrapper for a $1d$ \texttt{deal.II}-DoFHandler.
\item \texttt{include/timeiterator.h} This class works as an iterator on the \texttt{TimeDoFHandler}.                 
\end{itemize}
\subsection{Wrapper classes}
\begin{itemize}
  \item \texttt{wrapper/dofhandler\underline{ }wrapper.h} A wrapper class for the \texttt{deal.II} DoFHandlers. This 
    class is needed to provide support for the \texttt{dim $= 0$} case and to have a uniform interface to 
    DoFHandler and HPDoFHandler.
  \item \texttt{wrapper/fevalues\underline{ }wrapper.h} {\bf Will be removed soon!}
  \item \texttt{wrapper/function\underline{ }wrapper.h} An interface that allows to use functions that depend 
    not only on space but also on time.
  \item \texttt{wrapper/mapping\underline{ }wrapper.h} An interface that allows to use \texttt{deal.II}-mappings as well as  \texttt{deal.II}-mapping collections depending of the DoFHandler in use. To this end, the class has a template parameter \texttt{DOFHANDLER}.
  \item \texttt{wrapper/preconditioner\underline{ }wrapper.h} Contains wrappers for several of the preconditioners
    in \texttt{deal.II}. This is required since unfortunately the preconditioners in \texttt{deal.II} have different
    interfaces for their initialization.
  \item \texttt{wrapper/snopt\underline{ }wrapper.h} An interface to the SNOPT fortran library. This is an additional
    wrapper to the one provided by SNOPT to allow automatic construction of the functions required 
    by SNOPT using our library.
  \item \texttt{wrapper/solutiontransfer\underline{ }wrapper.h} A wrapper for the SolutionTransfer class
    from \texttt{deal.II}. 
  \item \texttt{wrapper/dataout\underline{ }wrapper.h} A wrapper for the DataOut class from \texttt{deal.II}.
\end{itemize}
